```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(scales)  
library(ggcorrplot)
```

```{r}
thedata <- read.csv("online_shoppers_intention.csv")
```

```{r}
head(thedata)
```


```{r}
str(thedata)
```


```{r}
thedata$Revenue <- as.factor(thedata$Revenue) 
thedata$Weekend <- as.factor(thedata$Weekend) 
thedata$TrafficType <- as.factor(thedata$TrafficType)
thedata$OperatingSystems <- as.factor(thedata$OperatingSystems)
thedata$Browser <- as.factor(thedata$Browser)
thedata$Region <- as.factor(thedata$Region)
thedata$Administrative <- as.numeric(thedata$Administrative)
thedata$Informational <- as.numeric(thedata$Informational)
thedata$ProductRelated <- as.numeric(thedata$ProductRelated)

str(thedata)
```



```{r}
summary(thedata)
```

```{r}
sum(is.na(thedata))
sapply(thedata, function(x) sum(is.na(x)))
```

```{r}
dim(thedata)
```
```{r}
#addes one column for Revenue as numeric and Weekend as numeric to include them in the correlation matrix for visualization
revenue_num <-as.numeric(thedata$Revenue)
weekend_num <-as.numeric(thedata$Weekend)
thedata$weekend_num=weekend_num
thedata$revenue_num=revenue_num

str(thedata)
```


```{r}
variablesnum <- c("Administrative", "Administrative_Duration", "Informational", "Informational_Duration",	"ProductRelated",	"ProductRelated_Duration",	"BounceRates",	"ExitRates",	"PageValues",	"SpecialDay","revenue_num","weekend_num")
data2 <- (thedata[variablesnum])
cor(data2)
```




```{r}
variables_correlations <- cor(data2) 
ggcorrplot(variables_correlations,type="lower", lab = TRUE, lab_size = 2) + 
  ggtitle("Correlation between Numerical Features")
```
```{r}
outliersnum <-boxplot(thedata[1:9], las = 2, xlab ="")
outliersProductRelated_Duration <- boxplot(thedata$ProductRelated_Duration, horizontal = TRUE, outline = TRUE, main = "Boxplot for ProductRelated_Duration ")

outliersAdministrative_Duration <- boxplot(thedata$Administrative_Duration, horizontal = TRUE, outline = TRUE, main = "Boxplot for Administrative_Duration")

outliersInformational_Duration <- boxplot(thedata$Informational_Duration, horizontal = TRUE, outline = TRUE, main = "Boxplot for Informational_Duration ")

outliersProductRelated <- boxplot(thedata$ProductRelated, horizontal = TRUE, outline = TRUE, main = "Boxplot for ProductRelated ")

outliersPageValues <- boxplot(thedata$PageValues, horizontal = TRUE, outline = TRUE, main = "Boxplot for PageValues ")

temp <- c("Administrative","Informational","BounceRates","ExitRates","SpecialDay")
tempdata<-thedata[temp]
outlierstemp <-boxplot(tempdata, las = 2, xlab ="")

#out <- boxplot.stats(thedata$ProductRelated_Duration)$out
#out_ind <- which(thedata$ProductRelated_Duration %in% c(out))
#thedata[out_ind, ]

outlierscat <-boxplot(thedata[10:17], las = 2, xlab ="")

```


```{r}
#plots for numerical variables
library(ggplot2)

par(mfcol=c(2,2))


plot(thedata$Administrative,main="Plot of Administrative", col="blue")
plot(thedata$Administrative_Duration,main="Plot of Administrative_Duration")
plot(thedata$Informational,main="Plot of Informational")
plot(thedata$Informational_Duration,main="Plot of Informational_Duration")
plot(thedata$BounceRates,main="Plot of BounceRates")
plot(thedata$ExitRates,main="Plot of ExitRates")
plot(thedata$PageValues,main="Plot of PageValues")
plot(thedata$SpecialDay,main="Plot of SpecialDay")
plot(thedata$ProductRelated,main="Plot of ProductRelated")
plot(thedata$ProductRelated_Duration, main="Plot of ProductRelated_Duration")
```
```{r}
#For categorical variables

#par(mfcol=c(3,3))

plot(thedata$Revenue,main="Revenue")
plot(thedata$Weekend,main="Weekend")
plot(thedata$VisitorType,main="VisitorType")
plot(thedata$TrafficType,main="TrafficType")
plot(thedata$Browser,main="Browser")
plot(thedata$Region,main="Region")
```
```


```{r}
count(thedata, Revenue, name = 'Class.count')
```


```{r}
par(mfrow=c(1,2))
slices <- c(10422, 1908)
lbls <-c("False", "True")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct)
lbls <- paste(lbls,"%",sep="")
pie(slices, labels = lbls, main = "Class Revenue")

#This chart shows how the data is unbalanced, as we will try to answer how likely a customer will end up puchasing something or not
```



```{r}
sd_administrative<- sd(thedata$Administrative)
sd_Administrative_Duration<- sd(thedata$Administrative_Duration)
sd_Informational<- sd(thedata$Informational)
sd_Informational_Duration<- sd(thedata$Informational_Duration)
sd_ProductRelated<- sd(thedata$ProductRelated)
sd_ProductRelated_Duration<- sd(thedata$ProductRelated_Duration)
sd_BounceRates<- sd(thedata$BounceRates)
sd_ExitRates<- sd(thedata$ExitRates)
sd_PageValues<- sd(thedata$PageValues)
sd_SpecialDay<- sd(thedata$SpecialDay)
sd_administrative
sd_Administrative_Duration
sd_Informational
sd_Informational_Duration
sd_ProductRelated
sd_ProductRelated_Duration
sd_BounceRates
sd_ExitRates
sd_PageValues
sd_SpecialDay
```

```

```{r}
library(readr)
write_csv(thedata, path="C:/Users/gabri/Desktop/thedatacleanedOct9.csv")
```


          

              

